---
title: "Homework 4"
author: "Nancy Yeung (ny3257) - SDS 315 - [GitHub Repository](https://github.com/0NancyYeung0/Homework4.git)"
output: pdf_document
---
\vspace{-1cm}

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=3, fig.width=8, warning=FALSE, message=FALSE, echo=FALSE)
```

```{r}
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(kableExtra)
library(knitr)
library(tidyverse)
library(tibble)
library(boot)
library(mosaic)
GasPrices <- read.csv('gasprices.csv')
SClass <- read.csv('sclass.csv')
Ebay <- read.csv('ebay.csv')
NBCPilot <- read.csv('nbc_pilotsurvey.csv')
```
------------------------------------------------------------------------
\begingroup
\fontsize{12}{14}\selectfont
**Problem 1:**
\endgroup

\begingroup
\fontsize{10}{12}\selectfont
**Part A**
\endgroup

```{r}
ggplot(GasPrices, aes(x = Price, fill = Competitors)) + geom_histogram(binwidth = 0.1, position = "identity", alpha = 0.7) + labs(title = 'Frequency of Gas Prices Based on if there are Competitors in Sight', x = 'Price ($)', y = 'Frequency', fill = 'Competitors') + scale_fill_manual(values = c('pink', 'skyblue')) + theme_minimal() + theme(text = element_text(size = 13, family = "serif"))

BootDifference = do(10000) * diffmean(Price ~ Competitors, data = mosaic::resample(GasPrices))
```

There is a theory that gas stations charge more if they lack direct competition in sight. The mean difference between gas prices based on whether there are competitors within eye sight is approximately `r round(confint(BootDifference, level = 0.95)[6], 4)`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDifference, level = 0.95)[2], 4)` and `r round(confint(BootDifference, level = 0.95)[3], 4)`. The negative sign indicates that, on average, prices in the 'No Competitors' group are higher than the ones in the 'Competitors' group, therefore making the theory correct, though because the range includes 0 there is no statistical significance since the range of the difference can swing either negative or positive.

\begingroup
\fontsize{10}{12}\selectfont
**Part B**
\endgroup

```{r}
GasPrices$Income = GasPrices$Income/100000

ggplot(GasPrices) + geom_point(aes(x = Income, y = Price), color = 'skyblue') + labs(title = "Average Household Income of an Area vs. the Gas Station Prices") + theme_minimal() + theme(text=element_text(size = 13, family="serif"))

BootIncomePrice = do(10000)*lm(Price ~ Income, data=mosaic::resample(GasPrices))
```

There is a theory that gas stations charge more if the average household income of the area is higher. There is a positive relationship between average household income and the gas prices in the area with an approximate `r round(confint(BootIncomePrice, level = 0.95)[2, 6], 4)` increase in gas price for every $10,000 increased in the household income of the area, and the 95% confidence interval for this difference is approximately between `r round(confint(BootIncomePrice, level = 0.95)[2, 2], 4)` and `r round(confint(BootIncomePrice, level = 0.95)[2, 3], 4)`. This makes the theory true.

\begingroup
\fontsize{10}{12}\selectfont
**Part C**
\endgroup

```{r}
ggplot(GasPrices, aes(x = Price, fill = Stoplight)) + geom_histogram(binwidth = 0.1, position = "identity", alpha = 0.7) + labs(title = 'Gas Prices vs. At a Stoplight', x = 'Price ($)', y = 'Frequency', fill = 'Stoplight') + scale_fill_manual(values = c('pink', 'skyblue')) + theme_minimal() + theme(text = element_text(size = 13, family = "serif"))

BootDifference = do(10000) * diffmean(Price ~ Stoplight, data = mosaic::resample(GasPrices))
```

There is a theory that gas stations at stoplights charge more. The mean difference between gas prices based on whether it's at a stoplight is approximately `r round(confint(BootDifference, level = 0.95)[6], 4)`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDifference, level = 0.95)[2], 4)` and `r round(confint(BootDifference, level = 0.95)[3], 4)` The positive sign indicates that, on average, prices in the 'Stoplight' group are higher than the ones in the 'No Stoplight' group, therefore making the theory correct, though because the range includes 0 there is no statistical significance since the range of the difference can swing either negative or positive.

\begingroup
\fontsize{10}{12}\selectfont
**Part D**
\endgroup

```{r}
ggplot(GasPrices, aes(x = Price, fill = Highway)) + geom_histogram(binwidth = 0.1, position = "identity", alpha = 0.7) + labs(title = 'Gas Prices vs. Direct Highway Access', x = 'Price ($)', y = 'Frequency', fill = 'Highway') + scale_fill_manual(values = c('pink', 'skyblue')) + theme_minimal() + theme(text = element_text(size = 13, family = "serif"))

BootDifference = do(10000) * diffmean(Price ~ Highway, data = mosaic::resample(GasPrices))
```

There is a theory that gas stations with direct highway access charge more. The mean difference between gas prices based on whether it has direct highway access is approximately `r round(confint(BootDifference, level = 0.95)[6], 5)`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDifference, level = 0.95)[2], 5)` and `r round(confint(BootDifference, level = 0.95)[3], 5)` The positive number indicates that, on average, prices in the 'Access to Highway' group are higher than the ones in the 'No Access to Highway' group, therefore making the theory correct.

\newpage

\begingroup
\fontsize{10}{12}\selectfont
**Part E**
\endgroup

```{r}
GasPrices <- mutate(GasPrices, Brand == "Shell")

ggplot(GasPrices, aes(x = Price, fill = Brand == "Shell")) + geom_histogram(binwidth = 0.1, position = "identity", alpha = 0.7) + labs(title = 'Gas Prices vs. Shell-Brand', x = 'Price ($)', y = 'Frequency', fill = 'Brand is Shell') + scale_fill_manual(values = c('pink', 'skyblue')) + theme_minimal() + theme(text = element_text(size = 13, family = "serif"))

BootDifference = do(10000) * diffmean(Price ~ Brand == "Shell", data = mosaic::resample(GasPrices))
```

There is a theory that Shell charges more than all other non-Shell brands. The mean difference between gas prices based whether it is Shell brand or not is approximately `r round(confint(BootDifference, level = 0.95)[2], 5)`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDifference, level = 0.95)[3], 5)` and `r round(confint(BootDifference, level = 0.95)[4], 5)` The positive number indicates that, on average, prices for gas is higher if the gas station is Shell brand compared to non-Shell brand stations, therefore making the theory correct, though because the range includes 0 there is no statistical significance since the range of the difference can swing either negative or positive.

\

\begingroup
\fontsize{12}{14}\selectfont
**Problem 2:**
\endgroup

\begingroup
\fontsize{10}{12}\selectfont
**Part A**
\endgroup

```{r}
PartA <- SClass %>%
  filter(year == "2011") %>%
  filter(trim == "63 AMG")

BootMileage = BootMileage <- do(10000) * mean(~mileage, data = resample(PartA))
```

The average mileage of 2011 S-Class 63 AMGs that were hitting the used-car market is `r round(confint(BootMileage, level=0.95)[2], 2)` to `r round(confint(BootMileage, level=0.95)[3], 2)`.

\begingroup
\fontsize{10}{12}\selectfont
**Part B**
\endgroup

```{r}
PartB <- SClass %>%
  filter(year == "2014") %>%
  filter(trim == "550") %>%
  mutate(isBlack = color == "Black")

BootColor <- do(10000) * prop(~isBlack, data = resample(PartB))
```

The proportion of 2014 S-Class 550s that were painted black is `r round(confint(BootColor, level=0.95)[2], 2)` to `r round(confint(BootColor, level=0.95)[3], 2)`.

\

\begingroup
\fontsize{12}{14}\selectfont
**Problem 3:**
\endgroup

\begingroup
\fontsize{10}{12}\selectfont
**Part A**
\endgroup

```{r}
EdEarl <- NBCPilot %>%
  filter(Show == "Living with Ed" | Show == "My Name is Earl")

BootDifference = do(10000)*diffmean(Q1_Happy ~ Show, data=mosaic::resample(EdEarl))
```

The question I'm trying to answer is who makes people happier between the shows “Living with Ed” and “My Name is Earl”. I first filtered the dataset to get data only on these two shows, then used bootstrapping to estimate the difference in mean. TThe difference of happiness ratings is `r round(confint(BootDifference, level = 0.95)[6], 4)`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDifference, level = 0.95)[2], 4)` and `r round(confint(BootDifference, level = 0.95)[3], 4)`. The range includes 0 meaning there is no statistical significance and we can't say for certain which show makes people happier since the range of the difference can swing either negative or positive.

\begingroup
\fontsize{10}{12}\selectfont
**Part B**
\endgroup

```{r}
LoserLA <- NBCPilot %>%
  filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")

BootDifference = do(10000)*diffmean(Q1_Annoyed ~ Show, data=mosaic::resample(LoserLA))
```

The question I'm trying to answer is between the shows “The Biggest Loser” and “The Apprentice: Los Angeles”, which makes people the most annoyed. I first filtered the dataset to get data only on these two shows, then used bootstrapping to estimate the difference in mean. The difference of annoyance ratings is `r round(confint(BootDifference, level = 0.95)[6], 4)`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDifference, level = 0.95)[2], 4)` and `r round(confint(BootDifference, level = 0.95)[3], 4)`. The negative number suggests that the average annoyance rating for “The Biggest Loser” to be lower than the ratings for “The Apprentice: Los Angeles”, therefore, The Apprentice: Los Angeles” is the show that makes people more annoyed by `r round(confint(BootDifference, level = 0.95)[6], 4)`.

\begingroup
\fontsize{10}{12}\selectfont
**Part C**
\endgroup

```{r}
Dancing <- NBCPilot %>%
  filter(Show == "Dancing with the Stars")
BootDancing = do(10000) * prop(~Q2_Confusing, data = resample(Dancing)) 
```

The question I'm trying to answer is what proportion of American TV watchers would we expect to give the show, "Dancing with the Stars", a "confusing" rating. I first filtered the data to create a new dataset with only information about  "Dancing with the Stars", then used bootstrapping to estimate the proportion of "confusing" ratings. The proportion of the viewers of "Dancing with the Stars" that would give a response of 4 or greater indicating "confusing" is `r round(confint(BootDancing, level = 0.95)[6], 4) * 100`, and the 95% confidence interval for this difference is approximately between `r round(confint(BootDancing, level = 0.95)[2], 4) * 100` and `r round(confint(BootDancing, level = 0.95)[3], 4) * 100`. 

\

\begingroup
\fontsize{12}{14}\selectfont
**Problem 4:**
\endgroup

\begingroup
\fontsize{10}{12}\selectfont
**Part A**
\endgroup

```{r}
BootDifference = do(10000) * diffmean(rev_ratio ~ adwords_pause, data = mosaic::resample(Ebay))
```

I am investigating whether there is a significant difference in revenue ratios between the control and treatment groups, which would indicate the impact of Google AdWords advertising on EBay's revenue. The treatment group had advertising paused for a month, while the control group remained as normal. I used bootstrapping to resample and estimate the distribution of the mean revenue ratio for both the control and treatment groups after filtering them. The difference in means was then calculated, and a 95% confidence interval was generated using the bootstrap samples. The mean difference in revenue ratios is negative, `r round(confint(BootDifference, level = 0.95)[6], 4)`, indicating that, on average, the control group has a higher revenue ratio compared to the treatment group, with the 95% confidence interval being `r round(confint(BootDifference, level = 0.95)[2], 4)` to `r round(confint(BootDifference, level = 0.95)[3], 4)`. The numbers suggests that, during the period of the experiment, EBay experienced a higher revenue ratio in the DMAs where Google AdWords advertising was not paused (control group) compared to the DMAs where advertising was paused (treatment group). This provides evidence that Google AdWords advertising contributes positively to EBay's revenue. 